Modelling Stochastic Time Delay Structures for Regression

### 2021-02-14 documentation/article/article.tex
Typo fix

In addition, by incorporating these elements we could begin to explore alternative forms of time series prediction. Essentially, existing prediction mechanisms predict the average across time shifts.However in some situations, the predictions could be considered nonsensical.

>>>>

In addition, by incorporating these elements we could begin to explore alternative forms of time series prediction. Essentially, existing prediction mechanisms predict the average across time shifts.However, in some situations the predictions could be considered nonsensical.
